% !TeX root = ../../main.tex
\section{Detailed operating cost breakdown}
The following sections de
\subsection{Raw material cost}
\label{sec:opex-raw-material}
Table XX displays the annual cost of raw materials incurred by Nitroma. The unit costs of raw materials in Year 1 are obtained from the negotiated price agreement with DEdwards Corp plc found in Section XX. For future costs, a cost escalation factor of 2.6\% is applied to account for inflation in China (XX). This is reflected on Nitroma’s financial statements in Section XX.

\subsection{Catalyst cost}
Table XX displays the annual cost of catalyst incurred by Nitroma. The unit costs of catalyst in Year 1 are obtained from the negotiated price agreement with DEdwards Corp plc found in Section XX. The quantities of catalyst needed are estimated using XX and a replacement frequency of 2 times per year (XX). The cost escalation factor used in Section \ref{sec:opex-raw-material} is repeated here for future catalyst cost projections in Nitroma’s financial statements.  

\subsection{Utility cost}
Table XX displays the annual cost of utilities incurred by Nitroma. The unit costs of utilities in Year 1 are obtained from the negotiated price agreement with DEdwards Corp plc found in Section XX. The quantities of cooling water and high-pressure steam are estimated using the heat duties of process units within the plant. Similarly, the electricity requirement is estimated by summing the power requirements of all process equipment. The cost escalation factor used in Section \ref{sec:opex-raw-material} is repeated here for future utility cost projections in Nitroma’s financial statements.  

\subsection{Labour cost}
As a continuous process, the plant must operate for 24 hours every day. Based on guidance from Towler \& Sinnott, three 8-hour shifts are planned, and five shifts team are hired to account for weekends and holidays (XX). Each shift team is made up of 4 process operators (mixed solids-fluids processing) and 1 general foreman to overlook affairs within the team. 2 process engineers are hired – one is trained to oversee the O-TOL production route and the other is trained to oversee the P-ABH production route. Both share joint responsibility over the P-ABA production route. 2 quality engineers are also hired with the same breakdown of responsibilities.  Similarly, 2 area supervisors are hired to manage affairs under their respective production route. The area supervisors report to 1 plant manager who is responsible for overseeing the entire plant. A managerial support team of 6 admin staff are hired with individual responsibilities including human resource management, finance, procurement, and sales. A team of 2 R\&D engineers is also hired to prepare for 5-yearly plant expansions. Table XX summarises Nitroma's labour costs.

The base wage for each job role was agreed with DEdwards Corp plc in the price agreement found in Section XX, based on the average wages in China. A 12.4\% loading factor was applied to the total labour cost to account for pensions, health insurance and other employee benefits in China based on data from UHY (XX). The annual labour costs for Nitroma are summarised in Table XX.

\subsection{Additional operating costs}
Table XX details additional costs incurred by Nitroma in operating the plant along with a brief note on the method of calculation, based on guidance from Towler \& Sinnott (XX).

\subsection{OPEX summary}