\section{Opportunities for advanced control}

\subsection{Model Predictive Control}
\subsubsection{Introduction}
Model Predictive control is an advanced control technique that can cope with complex multivariate control problems. A model predictive controller (MPC) functions by taking in current measurements of manipulated variables (MVs) and disturbances (DVs) from the plant and then calculates the future profile for the controlled variables (CVs) and constraint variables in order to predict the optimal values for the manipulated variables. The controller performs two sets of calculations, first to determine the future profile of CVs ('set-point calculations'), and second the optimal values for MVs ('control calculations') to reach the desired set-points. 

The future profile of CVs are calculated from solving an optimisation problem that determines the set points for the CVs for a period of time in the future ('prediction horizon'). The objective function for this optimisation is usually to maximise profit or minimise cost, and is subject to inequality constraints that can vary with time such as variations in process conditions, functional instrumentation and economic data such as pricing. These set-points are re-calculated each time new data is received. The optimal values for MVs are then calculated. Unlike traditional PID controllers, a sequence of MV steps are calculated by splitting the prediction horizon into a number of sampling intervals, and the effects on CVs are determined in order to move them closer to the desired set-points (see Figure \ref{fig:MPC}). 

The goal of the MPC is to minimise the differences between the set-point and the predicted values of the CV at each sampling instant. Expressing these errors in a vector to the MPC algorithm returns a combination of MV steps that minimises the total error. The MPC then outputs a signal to the actuators to implement the changes to the MVs. However, only the first step is performed. The MPC then receives new measurements from transmitters on the plant, and then re-calculates the trajectory of the CVs with an updated time horizon. In this way the MPC iteratively solves for the optimal MV action to bring the CV closer to its setpoint. 

The accuracy of MPC algorithms depends heavily on the dynamic model of the process it utilises for calculations. Assuming a good dynamic model exists, Model Predictive Control has serveral advantages over PID controllers, namely that it captures interactions between control loops, handles multiple inputs and predict multiple outputs, and takes into consideration physical constraints on actuators. 

\subsubsection{Application to Nitroma's plant}


\subsection{Real-time control}