\section*{Process control and design}

Operational safety and efficiency are at the core of Nitroma's business. To ensure production and quality targets are consistently met while mitigating safety risks, a robust and sophisticated control strategy, with sufficient protective structures, has been adopted.

A plant-wide control approach from \textcite{luyben_plantwide_1997} was adopted to design a control system capable of minimising disturbance propagation throughout the plant. The central architecture for the control system utilised PID controllers to enable constant monitoring and control of the plant. In addition, a robust controller was placed on the feed stream to the nitration reactor that can be manipulated to control the production capacity of our products, adding modularity to our plant.      

%Forty four process control structures were found to provide adequate disturbances management to achieve the design objectives. Control challenges and key maintenance issues along with associated mitigation strategies were discussed.

A detailed control architecture was designed around the plant section with the highest potential for damage, which was the 2-nitrotoluene hydrogenation reactor and downstream distillation column. Robust ratio and temperature controllers were designed using feedback, feedforward and cascade control arrangements to ensure the system can maintain optimum and safe operating conditions and respond to disturbances. Inferential temperature control was also cascaded onto the slow composition controller in the distillation column, to ensure robust quality control of the separation. Regular and executive alarms, linked to automated interlock actions, were integrated to the control structure as an additional layer of protection to respectively alert to operators of abnormal operation, and to bring the plant into a safe fail state. 

Nitroma's integrated network of automated controllers with additional layers of protection ensures the plant is capable of withstanding disturbances and can reliably, efficiently and safely operate. 



