\section*{Conclusion and recommendations}
Nitroma's continuous nitration plant is capable of an annual production of up to 650 tonnes of o-toluidine (\SI{95}{\percent} purity), up to 100 tonnes of 4-aminobenzoic acid (\SI{98}{\percent} purity) and up to 500 tonnes of 4-aminobenzaldehyde (\SI{98}{\percent} purity). Its modular plant design combines a thorough selection of product choices, along with novel designs of key process units, safety and environmental considerations and robust operational control to deliver a competitive and cutting-edge choice for continuous nitration. Nitroma's carefully selected products encompass a wide variety of end-uses such as in pharmaceuticals, agrochemicals and textiles that present opportunities to further penetrate a wide range of markets. Plant modularity provides Nitroma flexibility in adjusting the production according to market demand. Coupled with an inherently safer continuous design, Nitroma's plant presents itself as an attractive alternative to existing batch nitration processes.

Further improvement in Nitroma's design will be achieved by conducting pilot scales studies to evaluate the performance and scale-up potential of the designed process. Verification of kinetic and solubility data will also refine Nitroma's plant design. Alongside that, testing the automated control system and more detailed design will provide further confidence in its safe operation. Finally, wider market research will be conducted to further flesh out Nitroma's economic opportunity in China.

